Confidence Intervals for Prevalence Estimates from Complex Surveys with Imperfect Assays

### 2021-12-07 PrevAdjSurvey.tex
Ready for Mike's review

where  \( G_{\beta^*}^L \) and \( G_{\beta^*}^U \) are defined in Section~\ref{sec:weight-perfect}.

@@

where \( B_{KG}^L \) and \( B_{KG}^U \) are as defined in Section~\ref{sec:weight-perfect}.

@@

We compare properties our melded confidence interval WprevSeSp Poisson, to another melded confidence interval method WprevSeSp Binomial, and one method, wspoissonTest, which does not account for the imperfect assay.
The methods are assessed in a several simulated scenarios with varying levels of disease prevalence (0.5\% or 5\%), types of groups surveyed (50 groups 200 subjects or 8000 groups of 1 subject), distributions of weights among the groups (coefficient of variation from approximately 0\% to nearly 6\%), the number of groups with non-zero prevalence, and the specificity of the assay (80\% - 100\%).
In each scenario, the assay has 95\% sensitivity.
Each scenario is simulated 10,000 times, with new prevalence, sensitivity, and specificity surveys generated and 95\% confidence intervals are created.
Simulated sensitivity is assessed based on 60 tests, while specificity is based on 300 tests.

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_coverage_50_groups_0_005_prev.pdf}
\caption{Coverage properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal coverage, 95\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_coverage_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_coverage_8000_groups_0_005_prev.pdf}
\caption{Coverage properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal coverage, 95\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_coverage_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_coverage_50_groups_0_05_prev.pdf}
\caption{Coverage properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal coverage, 95\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_coverage_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_coverage_8000_groups_0_05_prev.pdf}
\caption{Coverage properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal coverage, 95\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_coverage_8000_groups_0_05_prev}
\end{figure}

Based on Figures~\ref{fig:imperfect_lower_error_frequency_50_groups_0_05_prev}--\ref{fig:imperfect_upper_error_frequency_8000_groups_0_05_prev}, we note that, in most settings, the naive wspoissonTest procedure results in extremely poor coverage, around 0\%, while the two melding procedures result in conservative confidence intervals, often nearing 100\% coverage.
With perfect specificity, the issue of poor coverage for the wspoissonTest procedure is less prominent, but the WprevSeSp Binomial method fails to maintain nominal coverage when the coefficient of variation among the weights is high.
Only our proposed WprevSeSp Poisson method maintains or exceed the desired coverage in all scenarios.
Because our methods appear to be very conservative, with coverage near 100\% in some cases, we present the widths of the confidence intervals in Figures~\ref{fig:imperfect_confidence_interval_width_50_groups_0_005_prev}--\ref{fig:imperfect_confidence_interval_width_8000_groups_0_05_prev}.
The WprevSeSp Binomial and  WprevSeSp Poisson methods typically produce wide intervals of approximately the same size - sometimes as wide as 12\%, even when true prevalence is 0.05\%.
One notable exception to this is presented in Figure \ref{fig:imperfect_confidence_interval_width_8000_groups_0_005_prev}, which shows that for tests with perfect specificity, the WprevSeSP produces much narrower confidence intervals than the other methods.

@@

We also apply these two methods to a real data set from \cite{Kali:2021}.
This data set was collected to estimate seroprevalence of SARS-CoV-2 in the United States between May and July 2020.
This test used in this data is estimated to have perfect sensitivity, based on 56 tests on individuals with confirmed SARS-CoV-2 and perfect specificity based on 300 tests on individuals confirmed to not have SARS-CoV-2.
First we apply the methods to the full data set (\( n =  8058, \text{weight coefficient of variation} = 252\%\)).
The Korn and Graubard type melded confidence interval (WprevSeSp Binomial) produced the 95\% confidence interval for population prevalence (2.53\%, 6.68\%), while the wsPoisson type melded confidence interval (WprevSeSp Poisson) produce the 95\% confidence interval (2.56\%, 7.54\%).
We also apply the wspoissonTest method from Section~\ref{sec:weight-perfect}, which does not account for imperfections in the assay, resulting in a 95\% confidence interval of (3.04\%, 7.39\%).
While all three intervals overlap to a large degree, the wsPoisson type melded confidence interval is the widest.
Our simulations show that the three procdures have similar coverage when specificity and weight coefficient of variation are both high, so this is unsurprising.

We also apply the methods to the subset of only Hispanic participants (\( n = 1281, \text{weight coefficient of variation} = 306\% \)).
The Korn and Graubard type confidence distributions (WprevSeSp Binomial) produce the 95\% confidence interval for population prevalence (2.35\%, 11.75\%), while the wsPoisson type confidence distributions (WprevSeSp Poisson) produce the 95\% confidence interval (2.40\%, 20.02\%).
The wspoissonTest method produces a 95\% confidence interval of (2.80\%, 19.63\%).
In this case, the two melded confidence intervals are much wider than the naive interval, as expected.
This is somewhat unexpected, but may be because prevalence is concentrated among respondents with lower weights, or be related to the smaller sample size used to measure prevalence, which is not reflected in our simulations.

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_lower_error_frequency_50_groups_0_05_prev.pdf}
\caption{Lower error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_lower_error_frequency_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_lower_error_frequency_50_groups_0_005_prev.pdf}
\caption{Lower error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_lower_error_frequency_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_lower_error_frequency_8000_groups_0_05_prev.pdf}
\caption{Lower error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_lower_error_frequency_8000_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_lower_error_frequency_8000_groups_0_005_prev.pdf}
\caption{Lower error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_lower_error_frequency_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_upper_error_frequency_50_groups_0_005_prev.pdf}
\caption{Upper error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_upper_error_frequency_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_upper_error_frequency_8000_groups_0_005_prev.pdf}
\caption{Upper error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_upper_error_frequency_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_upper_error_frequency_50_groups_0_05_prev.pdf}
\caption{Upper error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_upper_error_frequency_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_upper_error_frequency_8000_groups_0_05_prev.pdf}
\caption{Upper error properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_upper_error_frequency_8000_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_50_groups_0_005_prev}
\caption{Confidence interval width properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_confidence_interval_width_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_50_groups_0_05_prev}
\caption{Confidence interval width properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_confidence_interval_width_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_8000_groups_0_005_prev}
\caption{Confidence interval width properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_confidence_interval_width_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_8000_groups_0_05_prev}
\caption{Confidence interval width properties for the two melded confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson, and one method, wspoissonTest, which does not account for the imperfect assay.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_confidence_interval_width_8000_groups_0_05_prev}
\end{figure}

>>>>

where  \( G_{\beta^*}^L \) and \( G_{\beta^*}^U \) are defined in Section~\ref{sec:weight-perfect}.
We refer to this method as the WprevSeSp Poisson - weighted prevalence with sensitivity and specificity, where the prevalence confidence distribution is based on the weighted sum of Poissons.

@@

where \( B_{KG}^L \) and \( B_{KG}^U \) are as defined in Section~\ref{sec:weight-perfect}.
We refer to this as WprevSeSp Binomial - weighted prevalence with sensitivity and specificity, where the prevalence confidence distribution is based on a binomial variance assumption.

@@

We compare properties our melded confidence interval WprevSeSp Poisson, to another melded confidence interval method WprevSeSp Binomial, and one method, wsPoisson, which does not account for the imperfect assay.
The methods are assessed in a several simulated scenarios with varying levels of disease prevalence (0.5\% or 5\%), types of groups surveyed (50 groups 200 subjects or 8000 groups of 1 subject), distributions of weights among the groups (coefficient of variation from approximately 0\% to nearly 6\%), the number of groups with non-zero prevalence, and the specificity of the assay (80\% - 100\%).
In each scenario, the assay has 95\% sensitivity.
Each scenario is simulated 10,000 times, with new prevalence, sensitivity, and specificity surveys generated and 95\% confidence intervals are created.
Simulated sensitivity is assessed based on 60 tests, while specificity is based on 300 tests.

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_coverage_50_groups_0_005_prev.pdf}
\caption{Coverage properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal coverage, 95\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_coverage_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_coverage_8000_groups_0_005_prev.pdf}
\caption{Coverage properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal coverage, 95\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_coverage_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_coverage_50_groups_0_05_prev.pdf}
\caption{Coverage properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal coverage, 95\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_coverage_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_coverage_8000_groups_0_05_prev.pdf}
\caption{Coverage properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal coverage, 95\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_coverage_8000_groups_0_05_prev}
\end{figure}

Based on Figures~\ref{fig:imperfect_lower_error_frequency_50_groups_0_05_prev}--\ref{fig:imperfect_upper_error_frequency_8000_groups_0_05_prev}, we note that, in most settings, the two melding procedures result in conservative confidence intervals, often nearing 100\% coverage.
With perfect specificity, the WprevSeSp Binomial method fails to maintain nominal coverage when the coefficient of variation among the weights is high.
Only our proposed WprevSeSp Poisson method maintains or exceed the desired coverage in all scenarios.
In these scenarios, we also assess properties of the wsPoisson procedure, which does not account for the the imperfect assay.
This method results in approximately 0\% coverage in any scenarios where specificity is less than perfect.
Because our methods appear to be very conservative, with coverage near 100\% in some cases, we present the widths of the confidence intervals in Figures~\ref{fig:imperfect_confidence_interval_width_50_groups_0_005_prev}--\ref{fig:imperfect_confidence_interval_width_8000_groups_0_05_prev}.
The WprevSeSp Binomial and  WprevSeSp Poisson methods typically produce wide intervals of approximately the same size - sometimes as wide as 12\%, even when true prevalence is 0.05\%.
One notable exception to this is presented in Figure \ref{fig:imperfect_confidence_interval_width_8000_groups_0_005_prev}, which shows that for tests with perfect specificity, the WprevSeSP produces much narrower confidence intervals than the other methods.

@@

We also apply these two methods to a real data set from \cite{Kali:2021}.
This data set was collected to estimate seroprevalence of SARS-CoV-2 in the United States between May and July 2020.
This test used in this data is estimated to have perfect sensitivity, based on 56 tests on individuals with confirmed SARS-CoV-2 and perfect specificity based on 300 tests on individuals confirmed to not have SARS-CoV-2.
First we apply the methods to the full data set (\( n =  8058, \text{weight coefficient of variation} = 252\%\)).
The Korn and Graubard type melded confidence interval (WprevSeSp Binomial) produced the 95\% confidence interval for population prevalence (2.53\%, 6.68\%), while the wsPoisson type melded confidence interval (WprevSeSp Poisson) produce the 95\% confidence interval (2.56\%, 7.54\%).
We also apply the wsPoisson method from Section~\ref{sec:weight-perfect}, which does not account for imperfections in the assay, resulting in a 95\% confidence interval of (3.04\%, 7.39\%).
While all three intervals overlap to a large degree, the wsPoisson type melded confidence interval is the widest.
Our simulations show that the three procdures have similar coverage when specificity and weight coefficient of variation are both high, so this is unsurprising.

We also apply the methods to the subset of only Hispanic participants (\( n = 1281, \text{weight coefficient of variation} = 306\% \)).
The Korn and Graubard type confidence distributions (WprevSeSp Binomial) produce the 95\% confidence interval for population prevalence (2.35\%, 11.75\%), while the wsPoisson type confidence distributions (WprevSeSp Poisson) produce the 95\% confidence interval (2.40\%, 20.02\%).
The wsPoisson method produces a 95\% confidence interval of (2.80\%, 19.63\%).
In this case, the two melded confidence intervals are much wider than the naive interval, as expected.
This is somewhat unexpected, but may be because prevalence is concentrated among respondents with lower weights, or be related to the smaller sample size used to measure prevalence, which is not reflected in our simulations.

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_lower_error_frequency_50_groups_0_05_prev.pdf}
\caption{Lower error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_lower_error_frequency_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_lower_error_frequency_50_groups_0_005_prev.pdf}
\caption{Lower error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_lower_error_frequency_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_lower_error_frequency_8000_groups_0_05_prev.pdf}
\caption{Lower error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_lower_error_frequency_8000_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_lower_error_frequency_8000_groups_0_005_prev.pdf}
\caption{Lower error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal lower error rate, 2.5\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_lower_error_frequency_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_upper_error_frequency_50_groups_0_005_prev.pdf}
\caption{Upper error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_upper_error_frequency_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_upper_error_frequency_8000_groups_0_005_prev.pdf}
\caption{Upper error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_upper_error_frequency_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_upper_error_frequency_50_groups_0_05_prev.pdf}
\caption{Upper error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_upper_error_frequency_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_upper_error_frequency_8000_groups_0_05_prev.pdf}
\caption{Upper error properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
The horizontal dashed line indicates the nominal upper error rate, 2.5\%.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_upper_error_frequency_8000_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_50_groups_0_005_prev}
\caption{Confidence interval width properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 50 groups of 200 people are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_confidence_interval_width_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_50_groups_0_05_prev}
\caption{Confidence interval width properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 50 groups of 200 people are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_confidence_interval_width_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_8000_groups_0_005_prev}
\caption{Confidence interval width properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
Each point represents 10,000 simulations of datasets from a population with 0.5\% Prevalence where 8000 individuals are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_confidence_interval_width_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/imperfect_confidence_interval_width_8000_groups_0_05_prev}
\caption{Confidence interval width properties for the confidence interval procedures, WprevSeSp Binomial and WprevSeSp Poisson.
Each point represents 10,000 simulations of datasets from a population with 5\% Prevalence where 8000 individuals are sampled.
Each datasets also includes simulated results of tests to evaluate the sensitivity and specificity of the assay performed on 60 and 300 individuals, respectively.
Colored dashed lines are estimates from a logistic regression model using cubic splines.}
\label{fig:imperfect_confidence_interval_width_8000_groups_0_05_prev}
\end{figure}
